---
title: "Q Matrix Recovery Metrics"
author: "James Balamuta"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{q-matrix-metrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ecdmcore)
```

To assess the accuracy associated with estimating $\mathbf{Q}$ we employ both
matrix- and element-wise recovery rates across replication $r$. 
As the estimation is valid up to a permutation, we present the accuracy rates 
after permutating the estimated Q matrix across all trait (column) orderings.
Once the Q matrix has been permutated, we then compute and show
the respective metric.

**Matrix-wise recovery rate** is defined as:
$$
\frac{1}{R}\sum _{r=1}^R\mathcal I(\widehat{{Q}}^{(r)}=\widehat{Q})
$$

**Matrix-wise recovery rate** is defined as:
$$
\frac{1}{R}\sum _{r=1}^R\frac{1}{JK}\sum _{j=1}^J\sum _{k=1}^K\mathcal I(\hat{q}_{jk}^{(r)}=q_{jk})
$$
